Supporting Information

### 2017-02-07 code/rmarkdown/supporting-information.Rmd
+ update formatting
address some of the reviewers comments add in benchmark analysis
updated benchmark analysis

## Appendix S1
The reliable formulation explicitly considers the probability that planning units are inhabited by features. As a consequence, it may deliver prioritizations that will sufficiently represent an attribute space even if the features do not inhabit several of the planning units when the prioritization is implemented. This behavior is achieved by siting back-up planning units near selected planning units with low occupancy probabilities in the attribute space(s). To ensure that prioritizations are robust against multiple planning units being uninhabited, the problem assigns planning units at multiple backup levels.

@@

## Figures 
```{r, echo=FALSE, fig.height=8, fig.width=8.5, fig.cap='Attribute spaces used in the first case-study. Each panel shows a the distribution of a solution in environmental space and how it samples the realized niche for a different species. The left column of panels shows the solution generated using amount targets. The right column of panels shows the solution generated using amount and niche targets. Each column of panels corresponds to a different species. Hexagons show the distribution of demand points. The color of each heaxgon denotes the weighted frequency of demand points inside it. Points represent the environmental conditions associated with planning units inside the species geographic range that were selected for preservation in a given solution.'}
## prepare data
cs1.pu.niche.DF <- ddply(
	cs1.spp.DF,
	c('Species', 'Prioritisation'),
	function(x) {
		# init
		curr.prioritisation <- cs1.prioritisations[[as.character(x$Prioritisation)]]
		curr.spp.pos <- match(x$Species[1], curr.prioritisation@data@species[[1]])
		curr.sel.pos <- which(curr.prioritisation@data@attribute.spaces[[1]]@spaces[[curr.spp.pos]]@planning.unit.points@ids %in% which(as.logical(selections(curr.prioritisation))))
		# extract planning units
		curr.DF <- curr.prioritisation@data@attribute.spaces[[1]]@spaces[[curr.spp.pos]]@planning.unit.points@coords %>% as.data.frame()
		names(curr.DF) <- c('Niche1', 'Niche2')
		curr.DF$Species <-x$Species[[1]]
		curr.DF$Prioritisation <-x$Prioritisation[[1]]
		curr.DF$Solution <- 'discarded'
		curr.DF$Solution[curr.sel.pos] <- 'selected'
		# return data
		return(curr.DF)
	}
)
cs1.pu.niche.DF <- filter(cs1.pu.niche.DF, Solution=='selected')

@@

## Tables

>>>>

# Appendix S1
The reliable formulation explicitly considers the probability that planning units are inhabited by features. As a consequence, it may deliver prioritizations that will sufficiently represent an attribute space even if the features do not inhabit several of the planning units when the prioritization is implemented. This behavior is achieved by siting back-up planning units near selected planning units with low occupancy probabilities in the attribute space(s). To ensure that prioritizations are robust against multiple planning units being uninhabited, the problem assigns planning units at multiple backup levels.

@@

# Appendix S2

We conducted a benchmark analysis to understand how much time would be required to solve different sized conservation planning problems. Additionally, we also aimed to understand how the time required to solve a problem varied depending on which formulation was used (unreliable or reliable), and if fragmentation constraints were used.

## METHODS

We generated simulated data sets conservation planning problems using varying number of features `r paste(benchmark.params.LST$number.of.features, collapse=',')` and planning units (paste(benchmark.params.LST$number.of.planning.units, collapse=',')). For a given number of planning units and features, the data was simulated using the following steps. The planning units were simulated as squares that were arranged in a grid or near-grid like fashion. The units' costs were set to one. The spatial distribution of features were generated using binary spatially autocorrelated random fields [using the \texttt{RandomFields R} package; @rXXX]. If features were associated with less than two occupied planning units, these features were set to occupy two randomly selected planning units. All occupied planning units were set to have a probability of occupancy of `r benchmark.params.LST[[MODE]]$occupancy.probability`. Similar to the simulated data sets used in the main text, a geographic attribute space was used for each feature. The features' demand points were set as the centroids of the planning units that they occupied, and were weighted by the units' probability of occupancy. All problems used amount-based targets of `r benchmark.params.LST[[MODE]]$amount.target*100` % and space-based targets of `r benchmark.params.LST[[MODE]]$space.target*100`

We solved each conservation planning data set using the unreliable and reliable problem formulations (using default failure distance and level parameter) using no boundary length modifer, and using a boundary length modifier of `r max(benchmark.params.LST[[MODE]]$blm`. To assess variation in solve times, we generated and solved `r benchmark.params.LST[[MODE]]$replicates` random data sets per combination of number of features and planning units. All conservation planning problems were solved to within `r general.params.LST[[MODE]]$MIPGap * 100` % of optimality using Gurobi (version 7.0.0) and a an Intel(R) Xeon(R) CPU E5-2630 (version 3; 2.40 GHz). To provide comparable estimates for the typical user, problems were solved using `r as.english(general.params.LST[[MODE]]$threads)` threads.

## RESULTS

```{r, echo=FALSE, message=FALSE, fig.height=2, fig.width=2, fig.cap='insert caption here.'}
ggplot(benchmark.results.DF, aes(x=number.planning.units, y=time, color=number.features)) +
  geom_line() +
  facet_wrap(~ settings)
```

# Figures 
```{r, echo=FALSE, fig.height=8, fig.width=8.5, fig.cap='Attribute spaces used in the first case-study. Each panel shows a the distribution of a solution in environmental space and how it samples the realized niche for a different species. The left column of panels shows the solution generated using amount targets. The right column of panels shows the solution generated using amount and niche targets. Each column of panels corresponds to a different species. Hexagons show the distribution of demand points. The color of each heaxgon denotes the weighted frequency of demand points inside it. Points represent the environmental conditions associated with planning units inside the species geographic range that were selected for preservation in a given solution.'}
## prepare data
cs1.pu.niche.DF <- ddply(
	cs1.spp.DF,
	c('Species', 'Prioritisation'),
	function(x) {
		# init
		curr.prioritisation <- cs1.prioritisations[[as.character(x$Prioritisation)]]
		curr.spp.pos <- match(x$Species[1], curr.prioritisation@data@species[[1]])
		curr.sel.pos <- which(curr.prioritisation@data@attribute.spaces[[1]]@spaces[[curr.spp.pos]]@planning.unit.points@ids %in% which(as.logical(selections(curr.prioritisation))))
		# extract planning units
		curr.DF <- curr.prioritisation@data@attribute.spaces[[1]]@spaces[[curr.spp.pos]]@planning.unit.points@coords %>% as.data.frame()
		names(curr.DF) <- c('Niche1', 'Niche2')
		curr.DF$Species <-x$Species[[1]]
		curr.DF$Prioritisation <-x$Prioritisation[[1]]
		curr.DF$Solution <- 'discarded'
		curr.DF$Solution[curr.sel.pos] <- 'selected'
		# return data
		return(curr.DF)
	}
)
cs1.pu.niche.DF <- filter(cs1.pu.niche.DF, Solution=='selected')

@@

# Tables
